Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs

### 2020-10-13 paper/main.tex
Minor changes

\author{%
	Edouard~Leurent \\
	Inria Lille Nord-Europe \& Renault\\
	Paris, France\\
	\texttt{edouard.leurent@inria.fr} \\
	% examples of more authors
	 \And
	 Denis~Efimov \\
	 Inria Lille Nord-Europe, Valse team\\
	 Lille, France\\
	 \texttt{denis.efimov@inria.fr} \\
	 \And
	 Odalric-Ambrym~Maillard \\
	 Inria Lille Nord-Europe, SequeL team\\
	 Lille, France\\
	 \texttt{odalric.maillard@inria.fr} \\
}

@@

It is difficult to check the validity of the stability condition 2. since it applies to matrices $A_N$ produced by the algorithm rather than to the system parameters. A stronger but easier to check condition is that the polytope \eqref{eq:polytope} at some point becomes included in a set where this property is uniformly satisfied. For instance, if the features are sufficiently excited, the estimation converges to a neighbourhood of the true dynamics $A(\theta)$. This also allows to further bound the input-dependent \hlb{estimation error} term.

>>>>

\author{%
	Edouard~Leurent \\
	Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL, Renault\\
	F-59000 Lille, France\\
	\texttt{edouard.leurent@inria.fr} \\
	 \And
	 Denis~Efimov \\
	 Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL\\
	 F-59000 Lille, France\\
	 \texttt{denis.efimov@inria.fr} \\
	 \And
	 Odalric-Ambrym~Maillard \\
	 Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL\\
	 F-59000 Lille, France\\
	 \texttt{odalric.maillard@inria.fr} \\
}

@@

It is difficult to check the validity of the stability condition 2. since it applies to matrices $A_N$ produced by the algorithm rather than to the system parameters. A stronger but easier to check condition is that the polytope \eqref{eq:polytope} at some iteration becomes included in a set where this property is uniformly satisfied. For instance, if the features are sufficiently excited, the estimation converges to a neighbourhood of the true dynamics $A(\theta)$. This also allows to further bound the input-dependent \hlb{estimation error} term.
